Baseline centering problem

### 2018-11-26 paper/tangotd.tex

@@

TD is the only one of those fixed point equations that is
\emph{samplable} given that we can sample $\rho$, $\rho P$ and $\rho R$.
\footnote{Actually the minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is also samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, the $\rho^2$ is a bit weird... moreover having
$\transp{\Delta}\Delta$ means we are just facing the double sampling
problem.
}
Thus, from now on we are going to focus on solving
\begin{equation}
\transp{\Phi}\rho (\Id-P)V=\transp{\Phi}\rho R
\end{equation}
using various SGD-like solvers.

>>>>

Instead of applying the Dirichlet norm to $(V-(\Id-P)^{-1}R)$, one can
apply the inverse Dirichlet norm to $((\Id-P)V-R)$. When When $P$ is
reversible and $\rho=\mu$ this
is the same. One tries to minimize
$\transp{((\Id-P)V-R)}\rho\mathcal{D}^{-1}\rho((\Id-P)V-R)$ where
$\mathcal{D}\deq \rho+\rho'-\rho P-\transp{(\rho P)}$ as above, and use
TANGO to invert $\mathcal{D}$. However this suffers from a double
sampling problem.

@@

TD is the only one of those fixed point equations that is
\emph{samplable} given that we can sample $\rho$, $\rho P$ and $\rho R$.
\footnote{Actually the minimizer of the $L^2(\rho^2)$ error between $R$
and $(\Id-P)V$ is also samplable:
\begin{equation}
\transp{\Phi}\transp{(\Id-P)}\rho^2(\Id-P)V=\transp{\Phi}\transp{(\Id-P)}\rho^2
R
\end{equation}
however, the $\rho^2$ is a bit weird... moreover having
$\transp{\Delta}\Delta$ means we are just facing the double sampling
problem. Even the right-hand-side involves double sampling.

The minimizer of a weird norm $L^2(\rho \Phi\transp{\Phi}\rho)$ is better
samplable, because now it's enough to sample states \emph{with the same
features}, not just the exact same state. Use unclear. Should use a hash
of states instead.
}
Thus, from now on we are going to focus on solving
\begin{equation}
\transp{\Phi}\rho (\Id-P)V=\transp{\Phi}\rho R
\end{equation}
using various SGD-like solvers.
